Dirac neutrino mass generation from Majorana messenger

### 2019-07-29 draft.tex
sln

\begin{abstract}

We propose a two-Higgs-doublet model (THDM) for one-loop Dirac neutrino masses with Majorana mediators which can be dark matter candidates if they are the lightest states circulating the loop. This model is restricted by  neutrino physics,  lepton flavor violation and cosmological constrains, including  
the effective number light neutrinos $N_{\text{eff}}$ . Here we find that $M_{Z^{\prime}}/g^{\prime} \gtrsim 60\ \text{TeV}$ in order to satisfy the conditions of $N_{\text{eff}}$..
\end{abstract}

@@

The interpretation of neutrino experimental data in terms of neutrino
oscillations is compatible with both Majorana or Dirac neutrino masses
\cite{Tanabashi:2018oca}. The former possibility has received the most
attention but, given the lack of signals in neutrinoless double beta
decay experiments
\cite{KamLAND-Zen:2016pfg,Agostini:2018tnm,Aalseth:2017btx,Alduino:2017ehq,Albert:2017owj,Arnold:2016bed},
the latter cannot be dismissed. If neutrinos are Dirac particles, the
Standard Model (SM) particle content must be extended with
right-handed neutrinos, which can increase the effective
number of light neutrinos, $N_{\text{eff}}$, until 6. 
To be compatible with the current cosmological restrictions on
$N_{\text{eff}}$, only the  ps w l therm
To give small
masses to at least two Majorana or Dirac neutrinos, as required to
explain the neutrino oscillation experiments~\cite{Ahmad:2002jz,
  Fukuda:1998mi}, the seesaw mechanism with heavy fermions is usually
invoked. For the tree-level type-I seesaw we can have either light Majorana neutrinos with heavy Majorana mediators~\cite{Minkowski:1977sc,Yanagida:1979as,GellMann:1980vs,Mohapatra:1979ia} or light Dirac neutrinos with heavy Dirac mediators~\cite{Roncadelli:1983ty,Roy:1983be,Gu:2007mc,Ma:2014qra}. The radiative type-I seesaw includes both~\cite{} and~\cite{}, but now it is also possible to have light Majorana neutrinos with heavy  Dirac mediators~\cite{}. In this
work we want to explore the possibility to build a simple model with Dirac neutrino
masses and heavy  Majorana mediators. It is worth noticing that this idea have been already illustrated in
an extension of the minimal supersymmetric standard model~\cite{Demir:2007dt} but without show any explicit solution.

In models for Dirac neutrinos with some explanation for the smallness of
their masses, usually an adhoc discrete symmetry is invoked to forbid
the SM induced terms of Dirac at tree level and Majorana terms,
and discrete ad hoc symmetries are added~\cite{Han:2018zcn, Wang:2017mcy}.
In recent works, using symmetry ($B-L$) to forbid these terms without resorting
to discrete symmetries~\cite{Calle:2018ovc, Bonilla:2018ynb, Saad:2019bqf}.
In these cases, it is necessary to introduce new scalars and new Dirac or 
vector-like fermions, that are required to close the loop.

@@

>>>>

\begin{abstract}    
We propose a two-Higgs-doublet model (THDM) for one-loop Dirac neutrino masses with Majorana mediators which can be dark matter candidates if they are the lightest states circulating the loop. This model is restricted by  neutrino physics,  lepton flavor violation and cosmological constrains, including  
the effective number light neutrinos $N_{\text{eff}}$ . Here we find that $M_{Z^{\prime}}/g^{\prime} \gtrsim 60\ \text{TeV}$ in order to satisfy the conditions of $N_{\text{eff}}$..
\end{abstract}

@@

The interpretation of neutrino experimental data in terms of neutrino
oscillations is compatible with both Majorana or Dirac neutrino masses
\cite{Tanabashi:2018oca}. The former possibility has received the most
attention but, given the lack of signals in neutrinoless double beta
decay experiments
\cite{KamLAND-Zen:2016pfg,Agostini:2018tnm,Aalseth:2017btx,Alduino:2017ehq,Albert:2017owj,Arnold:2016bed},
the latter cannot be dismissed. If neutrinos are Dirac particles, the
Standard Model (SM) particle content must be extended with
right-handed neutrinos, which can increase the effective number of
light neutrinos, $N_{\text{eff}}$, until 6.  To be compatible with the
current cosmological restrictions on $N_{\text{eff}}$, the interaction
of the extra right-handed neutrinos with the primordial plasma must be
highly suppressed.  To give small masses to at least two Majorana or
Dirac neutrinos, as required to explain the neutrino oscillation
experiments~\cite{Ahmad:2002jz, Fukuda:1998mi}, the seesaw mechanism
with heavy fermions is usually invoked. For the tree-level type-I
seesaw we can have either light Majorana neutrinos with heavy Majorana
mediators~\cite{Minkowski:1977sc,Yanagida:1979as,GellMann:1980vs,Mohapatra:1979ia}
or light Dirac neutrinos with heavy Dirac
mediators~\cite{Roncadelli:1983ty,Roy:1983be,Gu:2007mc,Ma:2014qra}. The
radiative type-I seesaw includes both~\cite{} possibilities~\cite{}, but now it
is also possible to have light Majorana neutrinos with heavy Dirac
mediators~\cite{}. In this work we want to explore the possibility to
build a simple model with Dirac neutrino masses and heavy Majorana
mediators. It is worth noticing that this idea have been already
illustrated in an extension of the minimal supersymmetric standard
model~\cite{Demir:2007dt} but without show any explicit solution.

In models for Dirac neutrinos with some explanation for the smallness of
their masses, usually  adhoc discrete symmetries are invoked to forbid
tree level SM Dirac or Majorana mass terms,
and discrete ad hoc symmetries are added~\cite{Han:2018zcn, Wang:2017mcy}.
In recent works, using symmetry ($B-L$) to forbid these terms without resorting
to discrete symmetries~\cite{Calle:2018ovc, Bonilla:2018ynb, Saad:2019bqf}.
In these cases, it is necessary to introduce new scalars and new Dirac or 
vector-like fermions, that are required to close the loop.

@@

% Checl also:
$-2,6,-9,-3,7$
